Aggressive Scheduling for Numerical Programs

### 2012-05-02 report/draft.tex
Added conclusion and post mortem stuff. off to get a redbull.

\section{Surprises and Lessons Learned}
\begin{verbatim}
\end{verbatim}

\section{Conclusion}
\begin{verbatim}
+
+
+
+ Future work:
  - We have incorporated delays in our system, the question is can we use the
    results from hardware counters to determine the best values for these?
\end{verbatim}

@@

We propose distributing the credit as XX\% to Richard, XX\% to Flávio and XX\% to Berkin.
XXX Richard did this, Flavio did that, Berkin did ...

>>>>

\section{Surprises and Lessons Learned}
Initially, we were going to use a simulator to model processors and determine
how to map scheduling and unrolling parameters to the hardware
model. Unfortunately, we wildly underestimated the difficulty of simply
installing the simulator.

\section{Conclusion}
\begin{comment}
+
+
+
+ Future work:
  - We have incorporated delays in our system, the question is can we use the
    results from hardware counters to determine the best values for these?
\end{comment}
One of main limitations of APGS over expert programmers is that there are some
optimizations that could not be done effectively without sacrificing the level
of abstraction that such a system provides. The main limitation is that of
scheduling, and for computationally dense operations renders APGS useless over
experts. In this paper we demonstrated the effectiveness of schedule
instructions in an APGS while maintaining a high level of abstraction. We
achieved this goal in two steps. Firstly, we provided a mechanism for enforcing
a schedule at the C code level. Secondly, we implemented a software pipelining
transformation in SPIRAL. Through these two steps demonstrated significant
performance gains of an automatically generated and tuned computationally
dense operation on a variety of systems. This enhancement to SPIRAL is general
and can easily be extended to a large class of operations.

\subsection{Future Work}
First and foremost we wish to test a larger variety of automatically generated
operations. In particular, operations such as Matrix-Matrix Multiply stand to
gain significantly from our system.

Additionally, for the sake of the in-order systems such as the Atom, or those
with lengthy instruction, we plan on implementing some mechanism for delaying
instructions for arbitrary lengths.

Lastly, we wish to incorporate list scheduling in addition to software
pipelining. We suspect that the added granularity will open up further
opportunities for performance gains.

@@

We propose distributing the credit as 33\% to Richard, 33\% to Flávio and 33\% to Berkin.
Richard extended SPIRAL and devised the C scheduling mechanism, Flávio
implemented the benchmarks, Berkin set up the experiments.
